Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
revised section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{red}{It is worth mentioning that the steps described here are carried out shortly after the design of the solar photovoltaic system, as soon as the equipment and equipment specifications are defined; before buying and deploying them, as a way to ensure that the project will not fail.}

@@

\textcolor{red}{At this work, we estimated load curves based on survey and visiting performed in June of 2017, and the the estimated load curve was converted as vectors with 24 positions, one to each house of the day (in Watts): 
House 1: [118, 118, 118, 46, 46, 46, 95, 95, 170, 170, 296, 242, 242, 95, 95, 95, 95, 95, 342, 288, 288, 288, 288, 118]; 
House 2: [136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136]; 
House 3: [113, 113, 113, 113, 113, 113, 67, 67, 217, 97, 97, 97, 97, 97, 97, 97, 97, 97, 263, 113, 113, 113, 113, 113]; 
House 4: [207, 207, 207, 135, 135, 135, 66, 66, 161, 161, 233, 253, 248, 66, 66, 66, 66, 66, 302, 317, 322, 302, 302, 207]; 
House 5: [45, 16, 16, 16, 16, 16, 0, 0, 0, 72, 72, 222, 150, 150, 0, 0, 72, 72, 814, 814, 814, 742, 742, 16].}

>>>>

\textcolor{red}{Note that the steps described here are carried out shortly after the design of the solar PV system, as soon as the equipment and its specifications are defined, i.e., before buying and deploying them, as a safe approach to ensure that the project will succeed.}

@@

\textcolor{red}{In our study, we estimated load curves based on survey and visiting performed in June of 2017, and the the estimated load curve was converted as vectors with 24 positions, one to each house of the day (in Watts):}
%
\begin{itemize} 
\item \textcolor{red}{House 1: [118, 118, 118, 46, 46, 46, 95, 95, 170, 170, 296, 242, 242, 95, 95, 95, 95, 95, 342, 288, 288, 288, 288, 118];} 
\item \textcolor{red}{House 2: [136, 136, 136, 136, 136, 136, 67, 67, 184, 184, 184, 184, 184, 67, 67, 67, 67, 67, 253, 253, 253, 253, 253, 136];} 
\item \textcolor{red}{House 3: [113, 113, 113, 113, 113, 113, 67, 67, 217, 97, 97, 97, 97, 97, 97, 97, 97, 97, 263, 113, 113, 113, 113, 113];}
\item \textcolor{red}{House 4: [207, 207, 207, 135, 135, 135, 66, 66, 161, 161, 233, 253, 248, 66, 66, 66, 66, 66, 302, 317, 322, 302, 302, 207];} 
\item \textcolor{red}{House 5: [45, 16, 16, 16, 16, 16, 0, 0, 0, 72, 72, 222, 150, 150, 0, 0, 72, 72, 814, 814, 814, 742, 742, 16].}
\end{itemize}
